\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
Update related_work.tex

\section{Related Work}
\label{sec:related_work}
\hongyi{Move the stuff about USB protocol to Background}\\
\outline{Attack based on USB 1.0, briefly}\\
\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
\outline{Attack survey table}\\
\outline{Attack or current works about USB Type-C}\\

@@

\subsection{USB Attack}
\label{subsec:usb_attack}
While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.\hongyi{What?} One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky \cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter. What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique. These attacks are all using the vulnerabilities of USB protocol, but due to the limitations of USB 2.0, there are no port for video transferring in the devices with USB 2.0, so it is impossible to obtain the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios.

In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain}, \cite{stuxnet}, \cite{conficker} and \cite{flame} also attack with code injection. \cite{webcam}, \cite{malware},\cite{audioextraction}, \cite{usbee}, and \cite{turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices. Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.

Another kind of attacks for USB \cite{JFC} is to automatically record phone-screen and monitor user's input based on  the Mobile High-Definition Link(MHL) standard. With this approach, it is able to successfully exfiltrate data without the permission on user's side. Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary. Other attacks for USB to exfiltrate data\cite{smartphone}, \cite{poweremi},\cite{revealing}, \cite{su2017usb}, \cite{usbgpslocator}, \cite{bates2014leveraging}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer. In a similar way, \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

>>>>

\section{Related Work}
\label{sec:related_work}

@@

\subsection{USB Attack}
\label{subsec:usb_attack}
While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, accurate attacks couldn't be performed due to lack of user interface (UI). One means of attack is to crash the operating system with the property that the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique. But code injection and data exfiltrating would not work here.

\textbf{Attacks based on code injection and data exfiltrating: } \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain, stuxnet, conficker,flame} also attack with code injection. \cite{webcam, malware, audioextraction, usbee, turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices. Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.

\textbf{Attacks based on protocol masquerading:} Protocol masquerading is widely used to hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}. These works try to hide their own functionality with the re-written firmware when they are connected to the host, software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter. Due to the limitations of USB 2.0, there is no port for video transferring in the devices with USB 2.0, accurate attacks could not be performed without real-time feedback from the host, only environment fitted commands and scripts will work in these scenarios. \cite{JFC} is to automatically record phone-screen and monitor user's input based on the Mobile High-Definition Link(MHL) standard. With this approach, it is able to successfully exfiltrate data without the permission on user's side. Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.

\textbf{Attacks based on physical signal recovering:} Physical radio frequency always contains sensitive data, \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer. In a similar way, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
